A generalization of the Bradley-Terry model for draws in chess

### 2020-10-01 inst/jebo_chess_revision2.tex
citations on mental fatigue

\textcolor{DarkGreen}{The Bradley-Terry techniques used here furnish
  evidence that collusive games played during during Cura\c{c}ao 1962
  were less detrimental to future performance than noncollusive games.
  However, there was no cognitively realistic model for mental fatigue
  (for example, downweighting heavy workloads long in the past) and
  the criterion for restedness itself was quite coarse. not allowing
  It would be possible in principle to investigate the effect of
  recovery using similar reified entities.}

>>>>

\textcolor{DarkGreen}{The Bradley-Terry techniques used here furnish
  evidence that collusive games played during Cura\c{c}ao 1962 were
  less detrimental to future performance than noncollusive games.
  However, no cognitively realistic model for mental
  fatigue~\citep{boksem2008,linden2003} was used.  There was no
  allowance for recovery, for example; and the criterion for
  restedness itself was quite coarse.  It would be possible in
  principle to investigate such mechanisms using further reified
  entities.}
